### 2016-04-20 manuscript.Rnw
update manuscript to latest rotl version

The R programming language is a popular tool for phylogenetics and comparative
analysis. The R packages \texttt{ape} \citep{Paradis2004}, \texttt{phylobase}
\citep{phylobase-0.8.0}, \texttt{phangorn} \citep{schliep2011} and
\texttt{RNeXML} \citep{Boettiger2015} each provide functions to import and
manipulate trees within R and save the results in standard data
formats. Additional packages including \texttt{phytools} \citep{Revell2012},
\texttt{geiger} \citep{Pennell2014-geiger}, and \texttt{ggtree}
\citep{Yu-ggtree}, allow users to analyze and visualize data in a phylogenetic
context (see \url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list of phylogenetics packages in R). In addition to packages for
phylogenetic and comparative analyses, a growing number of R packages allows
users to query and access data from the web (e.g. \texttt{rFISHBASE}
\citep{Boettiger2012}, \texttt{rAvis} \citep{Varela2014}, and
\texttt{paleobioDB} \citep{Varela2015}), such that data associated with taxa in
a given phylogeny can be obtained directly in R.

@@

\texttt{rotl} gives users access to the endpoints provided by version 2 of the
APIs, and other versions of the APIs can be selected by the user as they become
available (version 3 is scheduled to be released at the end of March 2016). Two
other end-points are available in version 2 of the API: \emph{graph of life} and
\emph{collections}. Data from the \emph{graph of life} endpoint are not intended
for typical users, and will be removed in future releases. The \emph{collection}
endpoint is not fully functional, and no functions are available in the current
release of \texttt{rotl}. Future versions will make them available when the API
implements them.

>>>>

The R programming language is a popular tool for phylogenetics and comparative
analysis. The R packages \texttt{ape} \citep{Paradis2004}, \texttt{phylobase}
\citep{phylobase-0.8.0}, \texttt{phangorn} \citep{schliep2011}, and
\texttt{RNeXML} \citep{Boettiger2015} each provide functions to import and
manipulate trees within R and save the results in standard data
formats. Additional packages including \texttt{phytools} \citep{Revell2012},
\texttt{geiger} \citep{Pennell2014-geiger}, and \texttt{ggtree}
\citep{Yu-ggtree}, allow users to analyze and visualize data in a phylogenetic
context (see \url{https://cran.r-project.org/web/views/Phylogenetics.html} for a
comprehensive list of phylogenetics packages in R). In addition to packages for
phylogenetic and comparative analyses, a growing number of R packages allows
users to query and access data from the web (e.g. \texttt{rFISHBASE}
\citep{Boettiger2012}, \texttt{rAvis} \citep{Varela2014}, and
\texttt{paleobioDB} \citep{Varela2015}), such that data associated with taxa in
a given phylogeny can be obtained directly in R.

@@

\texttt{rotl} gives users access to the endpoints provided by version 3 of the
APIs, and other versions of the APIs can be selected by the user as they become
available.
